disaggregation: An \proglang{R} package for Bayesian spatial disaggregation modelling

### 2019-11-29 article.Rnw
Typo count to cases
Use cropped prepared data for direct use in the package

%
\begin{itemize}
\item {\textbf{Gaussian} ($\sigma_j$ is the dispersion of the polygon data)
\begin{equation} \label{eq:gaussian}
y_j \sim Normal(count_j/\sum agg_i, rate_j, \sigma_j)
\end{equation}
Here $\sigma_j = \sigma \sqrt{\sum agg_i^2} / \sum agg_i$, where  $\sigma$ is the dispersion of the pixel data (a parameter learnt by the model) }

@@

We then setup the data to use in the \pkg{disaggregation} package.

@@

API_path <- 'data/api_subnational.csv'
population_path <-'data/pop_at_risk_pf_2013.tif'
shapefile_path <- 'data/admin2019_2.shp'

covariate_raster_paths <- c(
  'data/MODIS_LST_Day.mean.5km.tif',
  'data/MODIS_EVI.mean.5km.tif',
  'data/SRTM_elevation.5km.mean.tif',
  'data/MODIS_LST_Day.SD.5km.tif')

# Make a RasterStack of covariates, 
# crop to the extent of Madagascar and scale values
covariates <- lapply(covariate_raster_paths, raster)
covariate_stack <- stack(covariates)
covariate_stack <- scale(crop(covariate_stack, extent(c(42, 52, -26, -10))))

# Read in the incidence data and only select data from Madagascar 2013
api <- read.csv(API_path)
api <- api[api$iso3 == 'MDG' & api$year == 2013, ]

# Read in the shapefile and only keep those that contain incidence data
shapes <- shapefile(shapefile_path)
shapes <- shapes[shapes$ID_2 %in% as.character(api$fdef_id), ]

# Add incidence information to the shapefile 
# (incidence count = API * population/1000)
indices <- match(shapes$ID_2, as.character(api$fdef_id))
shapes$inc <- (api$api_mean_pf[indices] * api$pop_at_risk_pf[indices])/1000

# Read in the population raster and crop it to the extent of Madagascar
population_raster <- raster(population_path)
population_raster <- crop(population_raster, extent(c(42, 52, -26, -10)))
@
%

>>>>

%
\begin{itemize}
\item {\textbf{Gaussian} ($\sigma_j$ is the dispersion of the polygon data)
\begin{equation} \label{eq:gaussian}
y_j \sim Normal(cases_j/\sum agg_i, rate_j, \sigma_j)
\end{equation}
Here $\sigma_j = \sigma \sqrt{\sum agg_i^2} / \sum agg_i$, where  $\sigma$ is the dispersion of the pixel data (a parameter learnt by the model) }

@@

We then read in the data to use in the \pkg{disaggregation} package.

@@

shapes <- shapefile('data/shapes/mdg_shapes.shp')
population_raster <- raster('data/population.tif')
covariate_stack <- getCovariateRasters('data/covariates', shape = population_raster)
@
%
